maxent model avec xvalidation

### 2019-04-05 src/maxent_avec_xvalidation.Rmd
horrible raster stack code!

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[1, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1)
  asclay$V2 <- as.character(asclay$V2)
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclaydep <- asclay$V1

@@

@@

>>>>

for (x in 1:nrow(depthlayers)){
  asclay <- depthlayers[x, ]
  asclay <- asclay[!is.na(asclay)]
  asclay <- as.data.frame(rbind(asclay))
  asclay$V1 <- as.character(asclay$V1)
  asclay$V2 <- as.character(asclay$V2)
  asclay$V3 <- as.character(asclay$V3)
  asclay$V4 <- as.character(asclay$V4)
  asclay$V5 <- as.character(asclay$V5)
  asclaydep <- asclay$V1

@@

ascdepth_list <- list.files(paste0("../output/maxent/predictions/", mth), glob2rx(pattern = "avg_*.asc"), full.names = TRUE)

asc120  <- raster(paste0("../output/maxent/predictions/", mth, "/avg_120.asc"))
asc41.18 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_41.18.asc"))
asc1.55586 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_1.55586.asc"))
asc1045.85 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_1045.85.asc"))
asc108.03 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_108.03.asc"))
asc11.7737 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_11.7737.asc"))
asc1151.99 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_1151.99.asc"))
asc1265.86 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_1265.86.asc"))
asc13.991 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_13.991.asc"))
asc133.076 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_133.076.asc"))
asc1387.38 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_1387.38.asc"))
asc147.406 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_147.406.asc"))
asc16.5253 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_16.5253.asc"))
asc163.165 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_163.165.asc"))
asc180.55 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_180.55.asc"))
asc19.4298 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_19.4298.asc"))
asc199.79 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_199.79.asc"))
asc2.66768 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_2.66768.asc"))
asc22.7576 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_22.7576.asc"))
asc221.141 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_221.141.asc"))
asc244.891 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_244.891.asc"))
asc26.5583 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_26.5583.asc"))
asc271.356 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_271.356.asc"))
asc3.85628 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_3.85628.asc"))
asc30.8746 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_30.8746.asc"))
asc300.888 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_300.888.asc"))
asc333.863 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_333.863.asc"))
asc35.7402 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_35.7402.asc"))
asc370.689 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_370.689.asc"))
asc411.794 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_411.794.asc"))
asc457.626 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_457.626.asc"))
asc47.2119 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_47.2119.asc"))
asc5.14036 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_5.14036.asc"))
asc508.64 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_508.64.asc"))
asc53.8506 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_53.8506.asc"))
asc565.292 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_565.292.asc"))
asc6.54303 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_6.54303.asc"))
asc61.1128 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_61.1128.asc"))
asc628.026 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_628.026.asc"))
asc69.0217 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_69.0217.asc"))
asc697.259 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_697.259.asc"))
asc77.6112 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_77.6112.asc"))
asc773.368 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_773.368.asc"))
asc8.09252 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_8.09252.asc"))
asc856.679 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_856.679.asc"))
asc86.9294 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_86.9294.asc"))
asc9.82275 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_9.82275.asc"))
asc947.448 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_947.448.asc"))
asc97.0413 <- raster(paste0("../output/maxent/predictions/", mth, "/avg_97.0413.asc"))

stackavg <- stack(asc120, asc41.18, asc1.55586, asc1045.85, asc108.03, asc11.7737, asc1151.99, asc1265.86, asc13.991, asc133.076, asc1387.38, asc147.406, asc16.5253, asc163.165, asc180.55, asc19.4298, asc199.79, asc2.66768, asc22.7576, asc221.141, asc244.891, asc26.5583, asc271.356, asc3.85628, asc30.8746, asc300.888, asc333.863, asc35.7402, asc370.689, asc411.794, asc457.626, asc47.2119, asc5.14036, asc508.64, asc53.8506, asc565.292, asc6.54303, asc61.1128, asc628.026, asc69.0217, asc697.259, asc77.6112, asc773.368, asc8.09252, asc856.679, asc86.9294, asc9.82275, asc947.448, asc97.0413)

sum <- calc(stkasc, fun = sum)
avg <- calc(stkasc, fun = mean)
  writeRaster(avg, (paste0("../output/maxent/predictions/", mth, "/avg_", mth, ".asc")), overwrite=TRUE)
  avgplot <- plot(avg, png(paste0("../output/maxent/predictions/", mth, "/avg_", mth, ".png"))) 
  dev.off()

@@

asc120
asc41.18
asc1.55586
asc1045.85
asc108.03
asc11.7737
asc1151.99
asc1265.86
asc13.991
asc133.076
asc1387.38
asc147.406
asc16.5253
asc163.165
asc180.55
asc19.4298
asc199.79
asc2.66768
asc22.7576
asc221.141
asc244.891
asc26.5583
asc271.356
asc3.85628
asc30.8746
asc300.888
asc333.863
asc35.7402
asc370.689
asc411.794
asc457.626
asc47.2119
asc5.14036
asc508.64
asc53.8506
asc565.292
asc6.54303
asc61.1128
asc628.026
asc69.0217
asc697.259
asc77.6112
asc773.368
asc8.09252
asc856.679
asc86.9294
asc9.82275
asc947.448
asc97.0413
